Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-16 1047_supp.tex
a

\section{More Denoising Results on the Real Noisy Images in Dataset \cite{ncwebsite}}
In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.\ As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method performs better than the state-of-the-art denoising methods.

@@

%------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------
\section{More Denoising Results on the 15 Cropped Images Used in \cite{crosschannel2016}}
In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig5}-\ref{fig9}, in most cases, our proposed method achieves better performance than the the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

>>>>

\section{More Denoising Results on the Real Noisy Images in Dataset \cite{ncwebsite}}
In this section, we give more comparisons of the state-of-the-art denoising methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.\ As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method performs better than the competing methods.

@@

%------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------
\section{More Denoising Results on the 15 Cropped Images Used in \cite{crosschannel2016}}
In this section, we provide more comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig5}-\ref{fig9}, in most cases, our proposed method achieves better performance than the the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
